Harnessing geo-located Tweets as a new geographical data source: Extracting mobility data from massive collection of geo-located Tweets

### 2016-02-29 Geo-located_Twitter_Data/latex/Geo_located_tweets.tex
new edits

\title{From massive collection of geo-located Tweets to a new geographical data source: Generating Twitter user mobility data from massive collection of geo-located Tweets}

@@

\section{Introduction}

disseminate

While today's pervasive social media platforms connects people in the virtual space.

The pervasive

The Location Based Social Media (LBSM)

Herewith known as Twitter

@@

\section*{Data collection}
In general, Twitter ({\tt{http://www.twitter.com}}) offers two kinds of search API

@@

@@

\begin{thebibliography}{10}

>>>>

\title{ Harnessing  geo-located Tweets as a new geographical data source: Extracting mobility data from massive collection of geo-located Tweets}

@@

\section{Introduction}
Understanding human mobility patterns is of great importance for a broad range of applications from urban planning~\cite{zheng2008}, traffic management~\cite{jiang2009}, and even the spatial spread of epidemic diseases~\cite{belik2011}.
However, the lack of detailed human movements with fine-grained spatial and temporal granularity limits the findings to capture mobility patterns of individuals~\cite{gonzalez2008,jurdak2015}.

Earlier research efforts relied on low resolution mobility data to understand human mobility patterns, such as using census records to understand human migration patterns~\cite{greenwood1985human}, or delivering questionnaires and asking volunteers to report the track of bank notes to infer human travel patterns~\cite{brockmann2006scaling}.

In addition to the mobility data collected by GPS trackers~\cite{zheng2008understanding, rhee2011levy} and mobile phone call records~\cite{gonzalez2008understanding,sevtsuk2010does,kung2014exploring}, 
emerging as a new source for mobility data, today's pervasive Location Based Social Media (LBSM) platforms (e.g., Twitter and Foursquare) offer continuous spatial Big Data streams with massive amount of detailed and frequently updated user digital footprints~\cite{thatcher2014living} in the form of real-world trails and footprints.
One significant advantage of LBSM data streams is the large spatial coverage, for example, researchers have used geo-located Twitter data for studying global mobility patterns~\cite{hawelka2014geo}, which is otherwise impossible by using other mobility datasets (e.g., GPS traces and mobile phone call records). 
In addition, the publicly available LBSM data streams offer unique opportunities for conducting reproducible scientific findings regarding the concerns of infringement on individual privacy, such as using mobile phone call records~\cite{giannotti2008mobility,crampton2014collect,Jurdak2015}.

However, there are some limitations and complexities in directly using the LBSM data for study human mobility patterns.

@@

Although Twitter allows users to gain access to the data streams, the obtained data cannot be shared directly with 
since the content of each Twitter message concerns user privacy. Therefore, when conducting research using Twitter data, one must download the data

The remainder of this paper is organized as follows. Section describes the

\section*{Data collection}
In general, Twitter ({\tt{http://www.twitter.com}}) provides two kinds of search APIs for retrieving Twitter messages:  REST API and Streaming API ({\tt{http://dev.twitter.com/overview/}}). 
Twitter REST API is used to search tweets that belong to a particular user account and its followers

@@

\subsection*{Data extraction based on geographical regions}

\subsection*{Constructing Twitter user space-time trajectories}

@@

\begin{thebibliography}{10}
\bibitem{zheng2008}
Zheng, Y., Li, Q., Chen, Y., Xie, X., and Ma, W.-Y. (2008). Understanding mobility based on gps data. In Proceedings of the 10th international conference on Ubiquitous computing, pp. 312-321. ACM.

\bibitem{jiang2009}
Jiang, B., Yin, J., and Zhao, S. (2009). Characterizing the human mobility pattern in a large street network. Physical Review E, 80(2):021136.

\bibitem{belik2011}
Belik, V., Geisel, T., and Brockmann, D. (2011). Natural human mobility patterns and spatial spread of infectious diseases. Physical Review X, 1(1):011001.

\bibitem{gonzalez2008}
Gonzalez, M. C., Hidalgo, C. A., and Barabasi, A.-L. (2008). Understanding individual human mobility patterns. Nature, 453(7196), pp.779-782.
